%!TEX root = exercisebank-doc.tex
\newversion{v0.0.2b11 2018/04/02}
  \change{Updated documentation syntax.}
\newversion{v0.0.3b38 2018/04/03}\nobreak
    \change{Updated triggers doc}
    \change{added trigger \dac{VeryBeginPartproblem}}

\newversion{v0.0.3b40 2018/04/03}
    \change{Added examples that uses the \refCom{At} command.}
    \change{Making front page and other snacks}

\newversion{v0.0.4b44 2018/04/03}
    \change{Changed design of part problems. (Looks much better now!)}

\newversion{v0.0.5b46 2018/04/03}
    \change{Fixed partproblems and solutions to fit on pages using \dac{filbreak}.}

\newversion{v0.1.0 2018/04/08}
    \change{Fixed title of documentation to match actual package.}
    \change{Fixed weird paragraph styling when displaying solutions}
    \change{Added a few package options. More to come!}

\newversion{v0.1.1 2018/04/13}
  \change{Added \refCom{exec}, which allows the user to execute macros between problems}
  \change{Bug fix: \refCom{At} would cause crash due to latexmk multiple builds}
  \change{Bug fix: \refCom{sprite} wouldn't build correctly}
  \change{Bug fix: misc bugs involving \refCom{makeset}, \refCom{buildset}, nohead and \refCom{phead}}

\newversion{v0.1.2 2018/04/17}
    \change{Fixed bug that \refCom{select} and \refCom{exclude} not working as expected.}
    \change{Added \refCom{ShowNumbers} for displaying numbers related to use in \refCom{select} and \refCom{exclude}}

\newversion{v0.1.3 2018/04/20}
    \change{Added custom dynamic figure path \refKey{figure root directory}.}
    \change{Fixed bugs related to \refCom*{phead} and the commands used in \refCom{makeset}-lists.}
\newversion{V0.1.4 2018/04/28}
    % \change{Introduced solutions only: \refCom{SolutionsOnly}}
    \change{Updated margins a lot!}
    \change{Fixed sneaky space in translation}
    \change{Fixed paragraph tightening when displaying solutions}
    \change{Introduced \refCom{DeclareExerciseCommand}}
    \change{Fixed bug with \refCom{exec}}
    \change{Iteration over items now uses a more lighweight approach.}
    \change{For commands that takes `lists' as arguments (\refCom{makeset}, \refCom{select} and \refCom{exclude}), the last item of the list can be terminated with new line or spaces without problems.}
    \change{For commands that takes `lists' as arguments, the entries in the list are now trimmed whitespaces on both sides.}
\newversion{v0.2.0 2018/07/21}
    \change{Fixed bug where \refCom{ppref} did not reference letter in part problem.}
    \change{Introducing \refCom{buildsets}-command for building more than one set at a time.}
    \change{Ability to add front page with the \refKey{front page} setup-key.}
    \change{You can now remove the forced margin setup with \refKey{style margins}.}
\newversion{v0.2.1 2018/09/24}
    \change{Added options for individual part problems using the \dac{nextproblem}-command}
    \change{Added tagging for part problems using using the \dac{nextproblem}-command and \dac{buildtags}-commands.}
    \change{Fixed problems related to \dac{ShowNumbers} not showing correctly.}
    \change{Fixed \dac{exec} so that it now can take paragraphs (made it \dac{long})}
    \change{Added point system}
    \change{Fixed bug where vertical space would remain when intro environment hidden}
    \change{\dac\DeclareExerciseCommand~now takes args}
    \change{Keys sent to \dac\makeset can now be sent to \dac\buildset~and~\dac\buildsets}
    \change{Introducing \dac\makesetdefaults}
\newversion{v0.2.2 2018/10/04}
    \change{Made trailing commas ignored in all lists (\dac\makeset,\dac\buildset,\dac\select,\dac\exclude, etc.)}
    \change{Fixed bug where tags wouldn't hide.}
\newversion{@@VERSION @@DATE}
    \change{Added possibility of custom part problem header from \dac\nextproblem}
    \change{Added possibility of showing problem only when \dac\DisplaySolutions active}
    \change{Corrected use of the length \dac\ppMarginBelow}
    \change{Fixed bug where \dac\phead and \dac\ShowFilenames crash}
    \change{Introduced \dac\SolutionsOnly}
\chlogtable


% Testers and thanks
\tester{\gh{thorstengrothe}}
\tester{\gh{tristelune1}}
